%------------------------------------------
% Resume for entry level Software Engineering roles
% Author : Abhishek Jha
% Github : https://github.com/abhijhacodes/latex-resume
% Website: https://abhijha.in
%------------------------------------------

\documentclass[a4paper,11pt]{article}

% --------------- PACKAGES -----------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
%% Font Definitions
\usepackage[sfdefault]{universalis}
\usepackage[T1]{fontenc}
\usepackage{microtype}

% ---------- RESUME FORMAT ADJUSTMENTS -------------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}[display] % ← here!
  {\raggedright\large}        % format
  {}                          % label
  {0pt}                       % sep
  {%
    \vspace{-22pt}             % gap
    \titlerule                % top rule
    \vspace{1pt}              % gap
  }
  [
    \vspace{-1pt}              % gap
    \titlerule                % bottom rule
    \vspace{-4pt}              % gap
  ]       

% \pdfglyphtounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[1]{
  \item[]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingNoItalics}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, nosep]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}


%-----------------RESUME STARTS HERE----------------------
% The resume has Education, Experience, Projects, Achievements, Technical Skills, Coding Profiles sections
% You can keep which all you want and in which order, comment the ones you don't need
% In ordering your sections, keep the ones first which are your best selling points

\begin{document}

\noindent % Prevents indentation
\begin{tabularx}{\textwidth}{@{} X c >{\raggedleft\arraybackslash}X @{}}
    \begin{tabular}{@{}l}
        \href{mailto:luispre99@gmail.com}{luispre99@gmail.com} \\
        (+52) 3317933872
    \end{tabular}
    & 
    \begin{tabular}[C]{@{}c}
        \bfseries\huge \textls[0]{Luis Enrique Preciado Muñiz} \\
    \end{tabular}
    &
    \begin{tabular}{@{}r}
        Guadalajara, México \\
        C.P 45200
    \end{tabular}
\end{tabularx}
\vspace{-14pt}
\begin{center}
    \href{https://lepcodes.vercel.app/}{\textcolor{BlueViolet}{\faGlobe\enspace \textbf{lepcodes.vercel.app}}} $|$  
    \href{https://www.linkedin.com/in/luispreciado/}{\textcolor{BlueViolet}{\faLinkedin\enspace \textbf{linkedin.com/in/luispreciado}}} $|$
    \href{https://github.com/lepcodes}{\textcolor{BlueViolet}{\faGithub\enspace \textbf{github.com/lepcodes}}}
\end{center}

% \vspace{10pt}
% \begin{center}
%     \textbf{\huge Luis Enrique Preciado Muñiz} \\ \vspace{8pt}
%     \faMapMarker\enspace \textbf{Guadalajara, México} $|$
%     \href{luispre99@gmail.com}{\textcolor{BlueViolet}{\faEnvelopeO\enspace \textbf{luispre99@gmail.com}}} $|$  
%     \href{https://www.linkedin.com/in/luispreciado/}{\textcolor{BlueViolet}{\faLinkedin\enspace \textbf{LinkedIn}}} $|$
%     \href{https://github.com/lepcodes}{\textcolor{BlueViolet}{\faGithub\enspace \textbf{Github}}} $|$
%     \small {\faMobile\enspace \textbf{+52 3317933872}}
% \end{center}
\vspace{-15pt}

%------------PROFILE------------
\rule{\textwidth}{0.1pt}

\vspace{1pt}
Analytical software developer with a strong background in machine learning and full-stack development. I dedicate my time to creating innovative solutions that solve complex problems and produce high-quality products.
\vspace{-5pt}

%-----------EXPERIENCE-----------
\section{\Large{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheadingNoItalics
      {\large Software Engineer Intern}{August 2023 -- July 2024}
      {\href{https://bosch.com.mx}{\textcolor{BlueViolet}{\textbf{\large{Robert Bosch México}}}}}{Guadalajara, México (Hybrid)}
      \resumeItemListStart
        \resumeItem{Designed and implemented a Python and Rasa framework-based Chatbot to facilitate new developer onboarding and provide troubleshooting assistance, complete with a local SQL database for response management, a ChatGPT-based model API for enhanced query handling, and Github for version control.}
        \resumeItem{Automating report generation for fault-mapping between customer defined fault application and ECU's  real monitors using Python scripts, leveraging Pandas, Anaconda, and fuzzy logic libraries, to ensure accurate tracking of monitor-fault mappings and to guarantee software quality deliverables.}
        \resumeItem{Developed scripts to cross-reference client requirements with ECU header files, identifying potential inconsistencies and streamlining the verification process.}
        \resumeItemNoBullet{\textbf{Key Metrics:} Enhanced quality of deliverables and improved efficiency by 40\%, reducing inconsistencies by 90\%.}
      \resumeItemListEnd
    \vspace{-2pt}
    \resumeSubheadingNoItalics
      {\large Robotics Intern}{Jun. 2022 - Aug. 2023}
      {\href{https://www.cucei.udg.mx/carreras/robotica/es/laboratorios/ciber-fisicos}{\textcolor{BlueViolet}{\textbf{\large{Intelligent Systems Laboratory}}}}}{Guadalajara, México}
      \resumeItemListStart
        \resumeItem{Supported the development of research on consensus algorithms for the Turtlebot robot platform and other holonomic robots using motion capture technology, optical tracking (OptiTrack), and ROS drivers on a Linux environment.}
        \resumeItem{Extensively worked with Linux in the assembly, programming, and testing of UAV units, as well as the implementation of monocular and stereoscopic visual-inertial odometry algorithms focused on indoor flights.}
        \resumeItem{Performed PCB and circuit design to synchronize measurements from optical and inertial sensors at the hardware level, which was required for the implementation of visual odometry.}
        \resumeItemNoBullet{\textbf{Key Metrics:} Modified existing ROS/ROS2 C++ drivers in a Linux environment to synchronize visual-inertial measurements and developed new drivers to control holonomic robots and UAV kinematics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------EDUCATION-----------
% Write only your two highest formal educational qualifications
\section{\Large{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Guadalajara}{Guadalajara, México}
      {Master's Degree in Machine Learning and Artificial Intelligence}{January 2025 -- Currently}
      \resumeItemListStart
        \resumeItem{Developing an EW-ACF-based forgetting mechanism for LSTM networks to optimize long-term memory retention in time-series forecasting systems through bio-inspired memory reset.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Guadalajara}{Guadalajara, México}
      {Bachelor's Degree in Robotics Engineering}{January 2020 -- June 2024}
      \resumeItemListStart
        \resumeItem{Bachelor's degree providing hands-on training in developing machine learning algorithms and robotic vision systems (Python, Matlab), designing and programming the underlying electronic circuits and embedded system (C/C++ and VHDL).}
      \resumeItemListEnd
    \resumeSubheading
      {CETI (Technical and Industrial Teaching Center)}{Guadalajara, México}
      {Automatic Control Technologist}{July 2017 -- April 2019}
      \resumeItemListStart
        \resumeItem{Degree providing extensive training in control theory, industrial instrumentation, and power electronics, with practical experience programming PLCs and embedded systems for automation tasks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{\Large{Projects}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\large{Chat React Component}} $|$ \emph{\href{https://lep-chat-demo.vercel.app/}{\textcolor{BlueViolet}{\textbf{Live}}}} $|$ \emph{\href{https://github.com/lepcodes/lep-chat}{\textcolor{BlueViolet}{\textbf{Github}}}}}{React, Next.js, Express, Tailwind CSS}
\resumeItemListStart
\resumeItem{Engineered a modular React chat component, serving as the core user interface for a Fitness AI Assistant web application built with Next.js.}
\resumeItem{Leveraged Tailwind CSS and CSS Modules to create a fully responsive, customizable, and visually appealing chat interface.}
\resumeItem{Integrated the component with a back-end Express API to handle conversational logic and data exchange.}
\resumeItem{\textbf{Key Skills:} Component-Based Architecture, State Management, API Integration, Responsive UI/UX.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\large{Omni-Control Driver}} $|$ \emph{\href{https://www.youtube.com/watch?v=NT2HuSaO69o/}{\textcolor{BlueViolet}{\textbf{Live}}}} $|$ \emph{\href{https://github.com/lepcodes/omni_control/}{\textcolor{BlueViolet}{\textbf{Github}}}}}{Python, OpenCV, ROS, C++, CMake, Bash}
\resumeItemListStart
\resumeItem{Developed a real-time C++ ROS driver for the robot's kinematics, achieving precise and responsive motion control.}
\resumeItem{Created and deployed Python-based neural control algorithms, enabling the robot to autonomously follow complex, pre-defined trajectories with high fidelity.}
\resumeItem{Integrated advanced capabilities including SLAM for real-time environment mapping and motion planning for obstacle avoidance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\vspace{-14pt}
\section{\Large{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, Javascript, Typescript, HTML, CSS, C/C++} \\
     \textbf{Technologies}{: Tensorflow, Pandas, React JS, Next JS, Node, Express JS, FastAPI, Tailwind, SQLite, PostgresQL, Supabase}  \\
     \textbf{Tools}{: Git, GitHub, Visual Studio Code} \\
    }}
 \end{itemize}


% --------CODING PROFILES--------------
% keep only your best coding profiles here
% add \\ after each 3rd profile to add a new line, if you add more profiles (which you shouldn't)
% \section{Coding Profiles}
% \renewcommand{\arraystretch}{0}
% \begin{tabular}{p{0.33\textwidth}p{0.33\textwidth}p{0.33\textwidth}}
%   \begin{itemize}[leftmargin=*, topsep=0pt]
%     \item LeetCode - \href{https://leetcode.com/username}{\textbf{\textcolor{BlueViolet}{username}}}
%   \end{itemize} &
%   \begin{itemize}[leftmargin=*, topsep=0pt]
%     \item Github - \href{https://github.com/username}{\textbf{\textcolor{BlueViolet}{username}}}
%   \end{itemize} &
%   \begin{itemize}[leftmargin=*, topsep=0pt]
%     \item HackerRank - \href{https://www.hackerrank.com/username}{\textbf{\textcolor{BlueViolet}{username}}}
%   \end{itemize} \\
% \end{tabular}


% -----------ACHIEVEMENTS/OPEN-SOURCE/RESEARCH-----------
% Keep achievements as per the company you are applying to
% If you have achievements in competitive programming, add it, it is useful when applying to product based companies
% You should give more priority to hackathons' and open source's achievements when applying for startups or abroad companies
% \section{Achievements}
% \resumeItemListStart
%     \resumeItem{Keep your relevant achievements only}
%     \resumeItem{Don't write about the art competitions you won in school or what was your rank in board exams, no one cares about that}
%     \resumeItem{Add \href{https://google.com/}{\textcolor{BlueViolet}{\textbf{link}}} to your achievements if you have, as a source of proof}
%     \resumeItem{\textbf{Highlight} the key points you want the other person to notice}
%     \resumeItem{Don't write that you were CR of your class in achievements, remember you are applying for a software engineering role}
% \resumeItemListEnd

%-------------------------------------------
\end{document}